% The master copy of this demo dissertation is held on my filespace
% on the cl file serve (/homes/mr/teaching/demodissert/)

% Last updated by MR on 2 August 2001

\documentclass[12pt,twoside,notitlepage]{report}

\usepackage{a4}
\usepackage{verbatim}

\input{epsf}                            % to allow postscript inclusions
% On thor and CUS read top of file:
%     /opt/TeX/lib/texmf/tex/dvips/epsf.sty
% On CL machines read:
%     /usr/lib/tex/macros/dvips/epsf.tex



\raggedbottom                           % try to avoid widows and orphans
\sloppy
\clubpenalty1000%
\widowpenalty1000%

\addtolength{\oddsidemargin}{6mm}       % adjust margins
\addtolength{\evensidemargin}{-8mm}

\renewcommand{\baselinestretch}{1.1}    % adjust line spacing to make
                                        % more readable

\begin{document}

\bibliographystyle{plain}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title


\pagestyle{empty}

\hfill{\LARGE \bf Tamas Sztanka-Toth}

\vspace*{60mm}
\begin{center}
\Huge
{\bf Cached Bug Prediction for Python repositories on GitHub} \\
\vspace*{5mm}
Computer Science Tripos - Part II \\
\vspace*{5mm}
Homerton College \\
\vspace*{5mm}
\today  % today's date
\end{center}

\cleardoublepage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Proforma, table of contents and list of figures

\setcounter{page}{1}
\pagenumbering{roman}
\pagestyle{plain}

\chapter*{Proforma}

{\large
\begin{tabular}{ll}
Name:               & \bf Tamas Sztanka-Toth                       \\
College:            & \bf Homerton College                     \\
Project Title:      & \bf Cached Bug Prediction for Python repositories on GitHub \\
Examination:        & \bf Computer Science Tripos - Part II, July 2016        \\
Word Count:         & \bf X\footnotemark[1]				 \\
Project Originator: & X                   \\
Supervisor:         & Advait Sarkar                    \\ 
\end{tabular}
}
\footnotetext[1]{This word count was computed
by {\tt detex diss.tex | tr -cd '0-9A-Za-z $\tt\backslash$n' | wc -w}
}
\stepcounter{footnote}


\section*{Original Aims of the Project}
Original aims of the project work were\cite{Git} \cite{SZZ}\cite{KimZim}\cite{KimZim}
\cite{FixCache}

\section*{Work Completed}

\section*{Special Difficulties}
 
\newpage
\section*{Declaration}

I, Tamas Sztanka-Toth of Homerton College, being a candidate for Part II of the Computer
Science Tripos, hereby declare
that this dissertation and the work described in it are my own work,
unaided except as may be specified below, and that the dissertation
does not contain material that has already been used to any substantial
extent for a comparable purpose.

\bigskip
\leftline{Signed }

\medskip
\leftline{Date }

\cleardoublepage

\tableofcontents

\listoffigures

\newpage
\section*{Acknowledgements}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% now for the chapters

\cleardoublepage        % just to make sure before the page numbering
                        % is changed

\setcounter{page}{1}
\pagenumbering{arabic}
\pagestyle{headings}

\chapter{Introduction}
\section{Motivation}
Why do I want to do this project?
\section{Aims of the project}
Summarizing this chapter, with stating what are the aims of the project.
\cleardoublepage
\chapter{Preparation}
\section{How does FixCache approaches bug-prediction}
Overview of the FixCache algorithm, in accordance with the original 2007 paper.
\subsection{Overview of FixCache algorithm}
\subsection{Variables}
\subsection{Hits vs. Misses}
\section{Using Git for FixCache}
\subsection{Introducing Git}
\subsection{Git workflow and branching}
\subsection{Repository backtracking with Git}
\section{Software engineering tools}
\subsection{Using Python}
\subsection{GitPython: the Python Git package}

\cleardoublepage
\chapter{Implementation}
\section{Design overview}
\subsection{Parsing module}
\subsection{File-management module}
\subsection{The repository module}
\subsection{Evaluation and Output}
\section{Core algorithm implementation}
\subsection{Identifying fixing commits}
\subsection{Commits which introduced a bug}
\subsection{The Repository class}
\subsection{Implementation difficulties}
\section{Bottleneck}
\subsection{What caused the initial enormous running time?}
\subsection{Speedup}

\chapter{Evaluation}
\section{Testing}
\section{Evaluation over hit-rate}
\subsection{The best cache-ratio}
\subsection{Optimal pre-fetch size variables}
\subsection{Differences between versions}
\section{Statistical analysis: how good is FixCache?}
\subsection{Algorithm performance over time} predictability of correctness. Differences in performances when changing the algorithm's parameters. 

\cleardoublepage
\chapter{Conclusion}

\cleardoublepage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% the bibliography

\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{refs}
\cleardoublepage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% the appendices
\appendix

\end{document}
